Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-04 doc/PRF2022/PRF_main.tex
yny

In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
and tune the boundary conditions with energy normalization to study the  collective dynamics of 
amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent, linear shear flow, and Taylor-Green flow).
Three quantities are computed to characterize the dynamics of the collective configurations of JPs: Free energy $F$, strain parameter $E$ and 
scalar order parameter $S_2$.

To overcome the well-known 
obstacle for numerical implementations in the free energy $F$ where the gradient of 
solution to the screened Laplace equation involves hyper-singularities, we derive the normal 
derivative \eqref{eq:normal_deriv} in terms of single layer potential $\SSS$.

Simulations include the self-assembly behaviors when the flow is absent and
when JP are subject to shear and TG background flows with various 
flow strengths. The free energy profiles demonstrate that the relaxation process for 
particles confined in a certain size of box is independent of number of particles 
($N_b$). However, the final configurations highly depend on the initial particle 
directors $\dd_i$. Therefore, multiple patterns or local energy minimum states may 
appear depending on the initial setup.

We track the total free energy, the orientational order parameter,
and the strain parameter to comprehensively summarize and classify the effective properties
of all three materials. 
Observations have shown that multi-lamella and the striated structures under a relatively 
weak linear shear flow behave like a rigid body with minimal deformation. The effective 
viscosity of the material gives a quantitative validation to support the statement. High 
shear-rate cases provide a range for critical shear rates where the structures break 
apart and undergo major topological changes. As expected in all case studies,
free energy, orientationl order, and strain combined 
are good topological indicators.

Under a TG flow, we examine the same measures and simulate all structures with 
the same criteria as ones in shear flow cases. In addition, for JP vesicle under a 
TG flow, we compare the results when the size of cell is varied and a nonmonotonic 
trend in reduced area with respect to the cell size arises. One finding to be noted is 
that the TG flow with specified parameters can effectively control the structure shapes 
such as a square vesicle or a polygonal shape.

The results reported here provide an inroad computational framework for colloidal sciences. 
The present study also helps us to understand more rheological properties of industrially 
produced JP.
This study can be extended to three dimensional systems 
and it has been included in our future goals\cite{kohl-cor-che-vee22}.
From a numerical perspective,
it is straightforward to include
random perturbations in the particle shape and
boundary condition that mimick interfacial properties
found in lab conditions\cite{Bradley2016,Bradley2017}.

>>>>

In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
and tune the boundary conditions with energy normalization to study the  collective dynamics of 
amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent flow, linear shear flow, and Taylor-Green flow).
Three quantities are computed to characterize the dynamics of the collective configurations of JPs: Free energy $F$, strain parameter $E$ and 
scalar order parameter $S_2$. In this numerical study we quantify how the collective hydrodynamics of JPs is affected by an external flow. 
Under a given flow, we use the three measures of deformations to quantify the differences in the collective dynamics between the three types of JPs.
These results, summarized below, may provide some general insight into the dynamic control of active particles in a viscous suspension.

Within the framework of boundary integral equations, we derive a convenient expression for computing the free energy using the single layer potential (see 
equation~\eqref{eq:normal_deriv}). In a quiescent flow, the free energy profiles demonstrate that the relaxation process for 
particles confined in a certain size of box is independent of number of particles 
($N_b$). However, we did find the final configurations to depend on the initial distribution of particle 
directors $\dd_i$. Therefore, multiple patterns or local energy minimum states may 
appear depending on the initial setup.

Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads.
For the multi-lamella (BC (ii)) and the striated (BC (iii)) structures  the assembly of JPs behaves like a rigid body with minimal deformation. The effective 
viscosity of the material gives a quantitative validation to support the statement. High 
shear-rate cases provide a range for critical shear rates where the structures break 
apart and undergo major topological changes. As expected in all case studies,
free energy, scalar order parameter, and strain combined 
are good topological indicators.

Under a Taylor-Green flow,  we find that the amphiphilic JPs to be most interesting, exhibiting different vesicle shapes depending on the ratio of the size of the
TG flow to the vesicle size. These results show that we can control the shape of the vesicle to be a square shape or a polygonal shape by adjusting the size of
the cell in TG flow. On the other hand, the assembly of multi-lamella JPs and the striated JPs behaves more or less as a rigid body with connected subdomains, with the number of subdomains increasing with stronger strength of the TG flow.

The results reported here provide an inroad modeling framework for hydrodynamics of active colloids. 
The present study also helps us understand the rheology of JP oligomers that may be realized in the experiments.
We are now extending this study to three dimensional systems with more realistic features such as size distributions of JPs
and thermal fluctuations.
%
 %it has been included in our future goals\cite{kohl-cor-che-vee22}.
From a numerical perspective,
it is straightforward to include
random perturbations in the particle shape and
boundary condition that mimick interfacial properties
found in lab conditions\cite{Bradley2016,Bradley2017}.
